Efficiently stable presentations from error-correcting codes

### 2023-09-05 efficient_stability.tex
cleared some comments, made small edits, left a couple more comments in Section 5

\hnote{I am wondering how exactly the comment above connects with the next theorem. For example, what is the ``direct product'' here? Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from? For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I tried, adding something above}

@@

Babai, Fortnow, and Lund essentially showed that \hnote{need to double check reference} $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$. \hnote{There is a slight difference in that BFL chooses the $t_0,\ldots,t_d$ randomly, whereas in what I wrote above, it's a fixed choice of points.}\tnote{Write this as a footnote? I thought they read the entire line} Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.

@@

\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}\tnote{added}

\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}\tnote{added above, if this what you meant?}

@@

\begin{proof}
Due to the test of the relations $\{R^\com_k\}$, it holds that 
\begin{align}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{a,b\in \F_2^t} \big\| [\phi(s_{u+t_i e_j,a}),\phi(s_{u+t_{i'} e_j,b})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{a,b\in \F_2^t} \big\| [\phi(s_{u,a}),\phi(s_{v,b})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
\end{align}
Now, for any $u,v\in \F_q^m$
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{a\in\F_2^t} (-1)^{a\cdot\kappa(\beta-\beta')} \Es{a'\in\F_2^t} (-1)^{a'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\Es{a,a'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{a'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{a\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{a'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
\end{align*}
\hnote{There seems to be some missing connective text between these two eqn blocks. Is it the commented out stuff below?}\tnote{fixed}
%Here, the second line follows since for $\beta,\beta'\in \F_q$, 
%\[ \Es{\alpha\in \F_q} (-1)^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
\begin{align*}
\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
&= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
&= \Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
\end{proof}

@@

\begin{proof}
First we show that the conclusion of Claim~\ref{claim:z2-stab-3} can be strengthened to hold for \emph{every} $z_0,\ldots,z_{d}$, instead of on average. To show this, note that for any $y_0,\ldots,y_d\in \F_q$ we can write 
\[ U_{0,z_0}\cdots U_{d,z_d}\,=\, U_{0,y_0}U_{0,z_0-y_0}\cdots U_{d,y_d}U_{d,z_d-y_d}\;.\]
By repeated application of Claim~\ref{claim:z2-stab-2b}, the term on the right-hand side satisfies 
\[ \big\| U_{0,y_0}U_{0,z_0-y_0}\cdots U_{d,y_d}U_{d,z_d-y_d}  - U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random. Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies 
\[ \big\| U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d} - \Big(\sum_{\alpha} \omega^{\tr(\sum y_i\alpha_i)} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} (-1)^{\tr(\sum (z_i-y_i)\alpha_i)} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $z_0,\ldots,z_d\in\F_q$, it holds that
\begin{equation}\label{eq:z2-stab-4-1}
 \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
	\end{equation}
	For any line $\ell \subset \F_q^m$, let $u_\ell\in \ell$ be chosen such that, for a uniformly random $\ell$ and conditioned on that $u_\ell$,~\eqref{eq:z2-stab-4-1} and~\eqref{eq:z2-stab-5-0} both hold, with right-hand side multiplied by a factor at most $2$. For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, define the operator $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell+t_0 e_j),\ldots,g(u_\ell+t_de_j)}$.
	Combining the two equations we deduce
	\begin{equation}\label{eq:z2-stab-4-2}
 \Es{\gamma\in\F_q} \Big\| U_{v,\gamma} -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
	\end{equation}
	\hnote{What does $U_v^\gamma$ mean?}\tnote{old notation; fixed} By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
\end{proof}

We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}. For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ is the code considered in Section~\ref{sec:rmq}. For the ``points measurement'' $A^u$ we choose $P^u$. For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}. Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}. By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that
\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$, with $r\geq 12mt$ an (arbitrary) integer. \hnote{what is the quantification on $r$? Is it for all $r \geq 12mt$, or for some $r \geq 12mt$?}\tnote{That's from our paper :) You get to choose $r$. That's what I meant by ``arbitrary''. Feel free to edit}

@@

In this section we give an application of our stability results to the problem of entanglement testing. We first introduce the language of nonlocal games. Then we associate a nonlocal game to any presentation of $\Z_2^t$. Finally, we show that, if the presentation is stable, then the game is a good entanglement test.

@@

\begin{definition}
Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that each span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$. 
\item (Soundness:) Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
\end{itemize}
\end{definition}

@@

\begin{proposition}\label{prop:rep-game}
Let $\code$ be an $[n,k,d]_2$ linear code, $M=(h,\nu)$ an $r$-local tester for $\code$, and $\mu$ the distribution defined above. Let $\strategy$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$. Then $\phi:x_i\mapsto {\widehat{P}}^{(\var,i)}$, for $i\in\{1,\ldots,n\}$, is an $(O(r\eps),\mu)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
\end{proposition}

@@

\begin{theorem}\label{thm:braiding}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.} 
\end{theorem}

@@

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $h_\bRM\in \F_2^{M\times N}$ be the parity check matrix for $\code_\bRM$ considered in Section~\ref{sec:eff-z2k}. Here, $N=q^{m+1}$ and $M=q^{m+2}(1+m)$. Let $\mu_R$ be the distribution on relations~\eqref{eq:z2k-eff} described in Section~\ref{sec:eff-z2k}. Execute either of the following tests with probability $1/4$ each. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item \textbf{Code test:} Identical to Figure~\ref{fig:braiding-test}.
    \item \textbf{(Anti-)commutation test:} Identical to Figure~\ref{fig:braiding-test}.
		 \item \textbf{Consistency test:} Identical to Figure~\ref{fig:braiding-test}.
		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$. and $W\in \{X,Z\}$ uniformly at random. 	
		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$ an 
		Sample a pair of questions $(x_c,y_c)$ as in the commutation game. If either question is $x_{X,0}$ or $x_{Z,0}$, replace it with $(W,\var,i)$ or $(W,\var,i')$ respectively. Otherwise, send the original question together with $\omega$, i.e.\ $(x_c,\omega)$ or $(y_c,\omega)$ respectively. Accept if and only if the players' answers are accepted in the commutation game.  
    \end{enumerate}
  \end{gamespec}
  \caption{The Pauli braiding test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
  \label{fig:pbt}

@@

\begin{proposition}
\label{prop:dim-test}
Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
\[
\dim(\mM) \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k~.
\]
\end{proposition}
\begin{proof}
If $\mM$ is infinite-dimensional, then we are done. Suppose instead it were finite-dimensional. Then $\mM$ must be (isomorphic to) a direct sum of finite-dimensional matrix algebras. Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.

>>>>

@@

Rubinfeld and Sudan~\cite{rubinfeld1996robust} (building on the work of Babai, Fortnow, and Lund~\cite{babai1991non}) showed that $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$. Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.

@@

@@

\begin{proof}
Due to the test of the relations $\{R^\com_k\}$, it holds that 
\begin{align}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{a,b\in \F_2^t} \big\| [\phi(s_{u+t_i e_j,a}),\phi(s_{u+t_{i'} e_j,b})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{a,b\in \F_2^t} \big\| [\phi(s_{u,a}),\phi(s_{v,b})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
\end{align}
Now, for any $u,v\in \F_q^m$
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{a\in\F_2^t} (-1)^{a\cdot\kappa(\beta-\beta')} \Es{a'\in\F_2^t} (-1)^{a'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\Es{a,a'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{a'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{a\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{a'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
\end{align*}
It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
\begin{align*}
\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
&= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
&= \Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
\end{proof}

@@

\begin{proof}
First we show that the conclusion of Claim~\ref{claim:z2-stab-3} can be strengthened to hold for \emph{every} $z_0,\ldots,z_{d}$, instead of on average. To show this, note that for any $y_0,\ldots,y_d\in \F_q$ we can write 
\[ U_{0,z_0}\cdots U_{d,z_d}\,=\, U_{0,y_0}U_{0,z_0-y_0}\cdots U_{d,y_d}U_{d,z_d-y_d}\;.\]
By repeated application of Claim~\ref{claim:z2-stab-2b}, the term on the right-hand side satisfies 
\[ \big\| U_{0,y_0}U_{0,z_0-y_0}\cdots U_{d,y_d}U_{d,z_d-y_d}  - U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random. Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies 
\[ \big\| U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d} - \Big(\sum_{\alpha} \omega^{\tr(\sum y_i\alpha_i)} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} (-1)^{\tr(\sum (z_i-y_i)\alpha_i)} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $z_0,\ldots,z_d\in\F_q$, it holds that
\begin{equation}\label{eq:z2-stab-4-1}
 \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
	\end{equation}
	For any line $\ell \subset \F_q^m$, let $u_\ell\in \ell$ be chosen such that, for a uniformly random $\ell$ and conditioned on that $u_\ell$,~\eqref{eq:z2-stab-4-1} and~\eqref{eq:z2-stab-5-0} both hold, with right-hand side multiplied by a factor at most $2$. For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, define the operator $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell+t_0 e_j),\ldots,g(u_\ell+t_de_j)}$.
	Combining the two equations we deduce
	\begin{equation}\label{eq:z2-stab-4-2}
 \Es{\gamma\in\F_q} \Big\| U_{v,\gamma} -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
	\end{equation}
	 By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
\end{proof}

We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}. For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ is the code considered in Section~\ref{sec:rmq}. For the ``points measurement'' $A^u$ we choose $P^u$. For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}. Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}. By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. %, with $r\geq 12mt$ an (arbitrary) integer.

@@

In this section we give an application of our stability results to the problem of entanglement testing in quantum information. We first introduce the language of nonlocal games. Then we associate a nonlocal game to any presentation of $\Z_2^t$. Finally, we show that, if the presentation is stable, then the game is a robust  entanglement test.

@@

\begin{definition}[Qubit test]
Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that each span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy $\strategy = \{P^{x}\}_{x \in \mX}$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$. 
\item (Soundness:) Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
Any synchronous strategy  $\strategy = \{P^{x}\}_{x \in \mX}$ on $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
\end{itemize}
\end{definition}

@@

\begin{proposition}\label{prop:rep-game}
Let $\code$ be an $[n,k,d]_2$ linear code, $M=(h,\nu)$ an $r$-local tester for $\code$, and $\mu$ the distribution defined above. Let $\strategy = \{P^{x}\}_{x \in \mX}$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$ \hnote{$G_{\code,m}$ vs $\G_{\code,M}$}. Then $\phi:x_i\mapsto {\widehat{P}}^{(\var,i)}$, for $i\in\{1,\ldots,n\}$, is an $(O(r\eps),\mu)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
\end{proposition}

@@

\begin{theorem}\label{thm:braiding}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound \hnote{I don't think quantum sound has been defined yet...do we mean to say stable?} and such that $(\code,M)$ is Abelian \hnote{What does it mean for the pair to be Abelian?}. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.} 
\end{theorem}

@@

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $h_\bRM\in \F_2^{M\times N}$ be the parity check matrix for $\code_\bRM$ considered in Section~\ref{sec:eff-z2k}. Here, $N=q^{m+1}$ and $M=q^{m+2}(1+m)$. Let $\mu_R$ be the distribution on relations~\eqref{eq:z2k-eff} described in Section~\ref{sec:eff-z2k}. Execute either of the following tests with probability $1/4$ each. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item \textbf{Code test:} Identical to that in Figure~\ref{fig:braiding-test}.
    \item \textbf{(Anti-)commutation test:} Identical to that in Figure~\ref{fig:braiding-test}.
		 \item \textbf{Consistency test:} Identical to that in Figure~\ref{fig:braiding-test}.
		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$. and $W\in \{X,Z\}$ uniformly at random. 	
		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$ an 
		Sample a pair of questions $(x_c,y_c)$ as in the commutation game. If either question is $x_{X,0}$ or $x_{Z,0}$, replace it with $(W,\var,i)$ or $(W,\var,i')$ respectively. Otherwise, send the original question together with $\omega$, i.e.\ $(x_c,\omega)$ or $(y_c,\omega)$ respectively. Accept if and only if the players' answers are accepted in the commutation game.  
    \end{enumerate}
  \end{gamespec}
  \caption{The Pauli braiding test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
  \label{fig:pbt}

@@

\begin{proposition}
\label{prop:dim-test}
Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test. Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
\[
\dim(\mM) \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k~.
\]
\end{proposition}
\begin{proof}
If $\mM$ is infinite-dimensional, then we are done. Suppose instead it were finite-dimensional. Then $\mM$ must be (isomorphic to) a direct sum of finite-dimensional matrix algebras. Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
